Biotic invasions fuck with the manageability of pollination networks

### 2017-01-10 paper/draft_2.Rmd
Update methods with daniel's comments

At the core of control theory of complex networks rests the idea that the state of a node depends on the state of the nodes it interacts with, and the particular form of this dependency is determined both by the dynamic relationship among interacting nodes as well as the structure of the links in the network. 
A large proportion of the recent advances on control theory have focused on linear systems as a first step to understand the controllability of nonlinear dynamics, in fact showing that fundamental can insight about the control of complex systems can be addressed without a detailed knowledge of the nonlinear dynamics and the system parameters [@Liu2015]. 
We therefore focus on complex networks whose dynamics can be locally linearised, at least near equilibium points, to the form $\frac{dx}{dt} = Ax + Bu(t)$, where the change over time of its state ($\frac{dx}{dt}$) depends on its current state *x* (the species' populations in an ecological context), an external time-varying input *u(t)*, and the matrices *A* and *B*, which encapsulate information about the network structure and how the network responds to the external input, respectively. 
Previous research has shown that such a system is controllable if there exists a minimum subset *D* of nodes in the network ($S > D \geq 1$, where *S* is the total number of species) to which to apply an external control signal that will propagate through the network and in turn drive the state of every other node in the network to a desired configuration in finite time [@Kalman1963; @Liu2011]. 
Conveniently, the information necessary to determine whether a network is controllable, and the number of driver nodes *D* is fully contained in the network structure [@Liu2011; @Motter2015].

We emphasise that, strictly speaking, the network structure tells us whether a linear approximation of the system is controllable or not, but it provides limited information about the characteristics of the control signal or the feasibility of its implementation [@Motter2015].
Despite this limitation, structural controllability provides a strong indication about our ability to control a system without requiring full and precise knowledge of the dynamical relationships among nodes.
This means that structural controllability can be applied to a wide range of readily available network representations of ecological communities. 
Moreover, wh show here how quantitative data about species interactions can help us move past some of the limitations of structural controllability by better approximating the role of dynamical relationships without being overly dependent on the specific choices of how these dynamics are modelled or characterised.

@@

The number of driver nodes *D* not only determines whether a network is controllable or not but can also provide a structural indication of how difficult its control might be.
This is because systems that require a large number of external input signals are intuitively more difficult or costly to control.
In an ecological context, external signals that modify the state of a node can be thought of as management interventions.
We therefore use the density of driver nodes $n_D = \frac{D}{S},$ as an index of the manageability of an ecological community.
From this perspective, the manageability of an ecological community can be understood in the context of how difficult is to modify the abundances of species in the community using external interventions—a common theme in ecosystem management, conservation, and restoration.

It has been recently shown that calculating *D* is equivalent to finding a maximum matching in the network [@Liu2011].
In a directed network, a *matching* consists of a subset of links in which no two of them share a common starting or ending node (Figure 1).
A given matching has *maximal cardinality* if the number of matched links (also referred to as the *matching size*) is the largest possible.
A maximal cardinality matching is then called a *maximum matching* if the sum of the weights of the matched links (also referred to as *matching weight*) is again the largest possible [@West2001].
Note that this implies that for unweighted binary networks all maximal cardinality matchings are also maximum matchings.

Once we have the subset of links that constitute a matching, we can also classify the nodes in the network (Figure 1).
A node is said to be *matched* if it is at the end of a matched link and *unmatched* otherwise. 
A node is also said to be *superior* if it is at the start of a matched link.
Note that a node cannot be superior if it has no outgoing links.
Notably, these node categories help us to intuitively link a maximum matching back to the concept of network controllability as follows.
Unmatched nodes are the driver nodes *D* because they have no superior in the network and must be directly controlled by an external input [@Liu2011].
Each matched node, on the other hand, can be controlled by the node that is pointing to it—its superior.

@@

While calculating *n~D~* provides an indication of the manageability of an ecological community, it does not provide information about the identity of the species that compose this set. 
This difference is rather important since maximum matchings are often not unique in a given network and different sets of species of size *D* could potentially be used to control the network [@Liu2011]. 
Ecologically, these distinctions are acutely relevant because management and conservation resources are limited and therefore ecological interventions should ideally be focused on the set of species that might provide the largest impact.
Consequently, we will show how species can be further characterised in terms of the frequency with which they exist on key paths leading through the network, which provides an indication of their relative importance in driving the state of the community.

Specifically, in an unweighted network to approximate a species importance for network control it is possible compute all the maximum matchings and calculate the frequency at which each species is classified as a superior node.
Because our networks are weighted, we compute all maximal cardinality matchings and not just the maximum matchings. 
We do so because empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011], and therefore using only maximum matchings in weighted empirical networks might be therefore too restrictive. 
Furthermore, we focus not only on driver nodes, as is customary in the control literature, but also on superior nodes because realistically, from an ecological perspective, we are not yet able to aim for full control of the abundances of all species in the community.
Superior nodes, of which driver nodes are a subset, are important for the controllability of the network not just because they might require an external control signal but, essentially, because they are part of the chain that transmits the control signal to other species.

It is worth to note that, traditionally, structural controllability assumes unweighted links—they exist or not—and hence results are entirely based on topology.
However, it has been shown that using weighted links can reveal important ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
By using the quantitative version of the maximum matching algorithm, we give priority to the species that participate in the pathways that potentially have the largest impact on the community; effectively incorporating, at least partially, the dynamics of the system.

@@

We then specified the structure of all networks using pollinator visitation frequency, which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@Vazquez2005; @Bascompte2006]. 
To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or pollinator importance as alternative measures of species interactions in a different data set that lacked invasive species [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all three of these options (Supplementary Information XXX).
Furthermore, because our approach depends to a large degree on the network topology, we evaluated the robustness of our results to undersampling.
Specifically, we removed links with a probability inversely proportional to its weight effectivelly simulating 
The sensitivity analysis indicated that the proposed methods can be applied even in the absence of complete sampling (Supplementary Information XXX).

@@

Given the different networks, we began by quantifying their manageability.
To do so, we calculated the maximum matching of the corresponding pollination network and determined the minimum proportion of species that need directed interventions to fully control the species abundances in the community. 
To simplify the analysis, we only considered the largest component in a network if it had more than one (two species are in different components if there exists no path between them and are hence independent of each other in terms of network control). 
Smaller components were present in eleven out of the twenty networks and were typically composed of just one plant and one pollinator. 
Their removal represented an average loss of `r sp_lost`% of the species and `r int_lost`% of the interactions.

@@

Recall that the aforementioned maximum matching algorithm requires a directed network in which a link between species *i* and *j* pointing to species *j* indicates that the abundance of *j* can be affected by the abundance of *i*.
This implies that we need first to identify a directionality for the links between species that is consistent with the dynamics of the community. 
In some ecological networks, establishing the directionality is relatively straightforward, for example when links represent biomass transfer or energy flow. 
Interspecific effects in pollination networks, however, are not strictly directed since the benefit is mutual between interacting species. 
Nevertheless, the relative extent to which a given pair of interacting species affect each other can be quantified by the magnitude of the mutual dependence [@Bascompte2006]. 
The dependency of plant *i* on pollinator *j*, *d~ij~*, is the proportion of the visits coming from pollinator *j* compared to all pollinator visits to plant *i*. 
Likewise, the dependency of pollinator *j* on plant *i*, *d~ji~*, is the ratio of the visits by pollinator *j* to plant *i* and all visits of pollinator *j*.
As the dependencies are not symmetric, its use generates a weighted bipartite network in which all interacting pairs are connected by two directed links (Figure 2b).

```{r figure 2, echo = F, fig.width = 6.2, fig.height = 1.6, message = F, warning = F, fig.pos = "T", fig.cap = "**Different ways to depict quantitative mutualistic networks**. (a) Pollination networks are typically described by the number of visits between each plant and animal species. (b) Given visitation data, the mutual dependencies between interacting species are calculated directly based on the relative visitation frequencies. (c) The relative differences of dependencies—the interaction asymmetry—then provide a means to identify the dominant direction of the interspecific effects."}

@@

Given the respective dependences, the extent to which a species $i$ affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry given by $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
Mutual dependencies have previously been shown to be highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa). 
This suggests that it may be possible to relax the assumption of bidirectional dependences further and simplify the network such that interacting species are connected by only one directed link when mutual dependencies are asymmetric (Figure 2c). 
Changing to unidirectional interactions determined by the observed direction of asymmetry, as a surrogate of bidirectional mutual dependences does not alter the relative *n~D~* of different networks (Supplementary Information XXX). 
Moreover, it confers an additional advantage for our purposes since it dramatically reduces the number of links in the network. 
This translates into a substantial reduction of the time and memory required for the computation of all possible maximum matchings in a network, particularly for large networks (see "Relative importance" subsection below).

#### Computational considerations

Finding the maximum matchings, especially in large, directed, and highly connected networks can be an expensive operation.
Although other less computationally expensive approaches to characterise the control profile of complex networks that are based on heuristics do exist [@Ruths2014], we found them to be extremely sensitive to assumptions regarding the direction of control (Supplementary Materials Section 2).
Our strategy, instead, is to adopt an alternative bipartite representation of the directed network in which the two levels indicate the outgoing and incoming links to each node (Supplementary Section XXX). 
Once we had this alternative representation, then used the maximum bipartite matching algorithm implemented in `igraph` [@Csardi2006a].

@@

Although understanding the variability of manageability across ecological networks is a useful result itself, we also wanted to test whether invasion status has an impact on the observed *n~D~*. 
We, therefore, used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also controlling for factors related to species richness, since one might naively expect to see a negative relationship between diversity and manageability [@Menge1995]. 
These covariates included the total number of species, plant richness, pollinators richness, the ratio of plants to pollinators richness, the link density (connectance), and the study site (as a two-level factor). 
We assessed competing models by comparing the Akaike Information Criterion corrected for small sample sizes (AICc), and report results for the most parsimonious model.

We next explored whether real networks differ in their architecture from random ones in a concerted way that affects manageability. 
Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it [@Liu2011], but the strength and applicability of this relationship have not been tested for in weighted ecological networks. 
We, therefore, compared the driver node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary. 
Randomisations were generated using vegan 2.3-3 [@Oksanen2016]. 
After generating the randomised networks, we then calculated the mutual dependences and interaction asymmetries of each and determined *n~D~*  using our maximum matching framework.
Finally, we calculated the average rank (akin to a p-value) of *n~D~* for each empirical network compared to the corresponding one of each set of 999 randomisations.

Beyond network structure, the dependency asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network *n~D~* results above. 
We, therefore, performed an additional randomisation in which we kept the structure of network constant but randomised the direction of the interaction asymmetries. 
That is, we first calculated the asymmetries for each community and then shuffled the direction of the link between each pair of species. 
Similar as to the other null models, we calculated the average rank of the empirical *n~D~* when compared to that of the randomisations.

@@

Our second key question is related to how species differ in their importance for driving the population dynamics of the community. 
To quantify this importance we computed all maximal cardinality matchings in each network. 
We then calculated the frequency with which each species is deemed to be a superior and a driver node in the set of matchings that had a total weight greater or equal to 0.5 times the weight of the maximum matching. 
We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions (mutual dependences and interaction asymmetries); however, the choice of this threshold had a negligible impact on the results (Supplementary Information XXX).

Although the species importance calculated from mutual dependences contains full information, even in sparse networks, like those studied here, the number of maximal matchings increases exponentially with the number of links and nodes in a network. 
Unfortunately, this means that the large number of links in the most diverse communities rendered the computation unfeasible when we used mutual dependencies. 
Taking this limitation into account, we compared the relative species ranks obtained when using asymmetries to those found when using mutual dependencies to test if they gave consistent results. 
The comparison was performed for eleven of the twenty networks (those for which the number of matchings was smaller than 4 x 10^10^), using a paired Spearman correlation test, a weighted correlation coefficient *r~w2~* [which gives more weight to higher ranks; @PintoDaCosta2015], and a Jaccard similarity of the driver species in both approaches. 
All three approaches identified a high similarity in relative ranks. 
Consequently, we focused on the results when using the asymmetries rather than mutual dependencies when further investigating the factors that determine species' relative importance since this also allows us to obtain results for all 20 networks.

#### Computational considerations

To compute all the maximum cardinality matchings we first generate the network's line graph—another representation in which nodes are the links of the original network and links represent common ending points [@West2001]. 
Then calculate the complement of this line graph, which generates a graph in which nodes are connected if and only if they are not connected in the line graph. 
Finally, all possible matchings of maximal size can be found by enumerating every clique (subgraphs in which all nodes are fully connected to each other) of maximum size in this complement graph [@Csardi2006a; @Gutin2013].
A graphical representation of this procedure can be found in Supplementary Information Fig XX.

@@

We then asked the question of whether some species-level structural properties can predict our metrics of species importance—the frequency to which a species is a driver or a superior node.
We used a set of generalised linear mixed-effects models (with binomial error structure) with the relative frequencies as the response variables. 
As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011]; two measures of strength of association and dependence (visitation and dependency strength), as their distribution determines the extent of interspecific effects [@Bascompte2006].
In addition, we also included guild and invasive status as categorical fixed effects; although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our data set did not contain enough variation to include the corresponding interactions terms for these latter two predictors. 
All network metrics were calculated using the R package bipartite 2.06 [@Dormann2008]. 
We lastly allowed for variation between different communities by including the network identity as a random effect [@Bates2015]. 
Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95% of the evidence [@Burnham2003; @Bates2015; @Barton2016]. 
Coefficient estimates were averaged following @Buckland1997a while confidence intervals were calculated following @Lukacs2010.

>>>>

Disregarding practical considerations, any network could, in theory, be fully controlled if we control the state of every single node individually.
At the core of control theory of complex networks, however, rest the idea the state of a node depends on the state of the nodes it interacts with, and the particular form of this dependence is determined both by the dynamic relationship among interacting nodes as well as the structure of the links in the network. 
This property can, therefore, be harnessed to find a minimum subset of driver nodes *D* to which to apply external input signals which then drive the state of every other node in the network to a desired configuration in finite time [@Kalman1963; @Liu2011].

Conveniently, the information necessary to determine whether a network with linear dynamics is controllable, and the minimum number of driver nodes *D* is fully contained in the network structure [@Liu2011; @Motter2015]. 
We, therefore, start from the assumption that that an ecological network can, at least near equilibrium points, be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change over time of its state ($\frac{dx}{dt}$) depends on its current state *x* (the species' populations in an ecological context), an external time-varying input *u(t)*, and the matrices *A* and *B*, which encapsulate information about the network structure and how the network responds to the external input, respectively. 
Even though this might be a strong assumption, it has been shown that fundamental insight about the control of complex systems can be gained without a detailed knowledge of the nonlinear dynamics and the system parameters [@Liu2015]; an important step towards understanding the controllability of systems with nonlinear dynamics [@Liu2011]. 
This means that this structural controllability can be applied to a wide range of readily available network representations of ecological communities to provide a strong indication of our ability to control them. 
Moreover, we show here how quantitative data about species interactions can help us move past some of the limitations of structural controllability by better approximating the role of dynamical relationships without being overly dependent on the specific choices of how these dynamics are modelled or characterised.

@@

The number of driver nodes *D* not only determines whether a network is controllable or not but can also provide a structural indication of how difficult its control might be.
This is because systems that require a large number of external input signals are intuitively more difficult or costly to control.
In an ecological context, external inputs that modify the state of a node can be thought of as management interventions.
Therefore, the density of driver nodes $n_D = \frac{D}{S},$ can be seen as a metric of the extent to which network structure can be harnessed for network control.
For instance, while a hypothetical "network" in which species do not interact but instead function independently from each other would require direct interventions in eversy single species to achieve full control, a linear food chain would require just one species to be directly controlled to knock-on cascading effects trough the trophic levels that compose it. 
From this perspective, it is possible to use *n~D~* as an index of the manageability of an ecological community, understood in the context of how difficult is to modify the abundances of species in the community using external interventions—a common theme in ecosystem management, conservation, and restoration.

It has been recently shown that calculating *D* is equivalent to finding a maximum matching in the network [@Liu2011].
In a directed network, a *matching* consists of a subset of links in which o two of them share a common starting or ending node (Figure 1).
A given matching has *maximal cardinality* if the number of matched links (also referred to as the *matching size*) is the largest possible.
A maximal cardinality matching is then called a *maximum matching* if the sum of the weights of the matched links (also referred to as *matching weight*) is again the largest possible [@West2001].
Note that this implies that for unweighted binary networks all maximal cardinality matchings are also maximum matchings.

Once we have the subset of links that constitute a matching, we can also classify the nodes in the network (Figure 1).
A node is said to be *matched* if it is at the end of a matched link and *unmatched* otherwise. 
A node is also said to be *superior* if it is at the start of a matched link.
Note that a node cannot be superior if it has no outgoing links.
Notably, these node categories are what help us to link a maximum matching back to the concept of network controllability as follows.
Unmatched nodes are the *driver nodes* *D* because they have no superior in the network and must be directly controlled by an external input [@Liu2011].
Each matched node, on the other hand, can be controlled by the node that is pointing to it—its superior.

@@

While calculating *n~D~* provides an indication of the manageability of an ecological community, it does not provide information about the identity of the species that compose this set. 
This difference is rather important since maximum matchings are often not unique in a given network and different sets of species of size *D* could potentially be used to control the network [@Liu2011]. 
Ecologically, these distinctions are acutely relevant because management and conservation resources are limited, and therefore ecological interventions should ideally be focused on the set of species that might provide the largest impact.
Consequently, species can be further characterised regarding the frequency with which an external input signal could be applied to them in order to control the full network. 
In other words, the frequency *f~D~* with which a species is classified as a driver node.
However, the role of driver nodes is still ambiguous when full network controllability is unfeasible or undesired—often the case in ecological settings.
Alternatively, species can also be characterised by the frequency *f~S~* with which they are classified as superior nodes.
This is, the frequency with which they exist on key paths through the network that transmits the control signal to other species.
We show how, together, *f~D~* and *f~S~* can provide an indication of a species' relative importance in driving the state of the community.

Most commonly, structural controllability assumes unweighted networks—links exist or not, and hence *f~D~* and *f~S~* can be calculated by computing all possible maximum matchings. 
However, it has been shown that using weighted links can reveal significant ecological patterns and processes that might be undetectable in unweighted networks [@Scotti2007; @Tylianakis2007; @Vazquez2007; @Kaiser-Bunbury2010a].
We, therefore, use a quantitative version of the maximum matching algorithm and instead calculate all maximal cardinality matchings and rank them by their matching weight. 
We do so because empirical interaction strengths are to some extent stochastic and depend on proximate factors such as sampling method and intensity [@Gibson2011], and therefore using only maximum matchings in weighted empirical networks might be therefore too restrictive. 
By incorporating the interaction weight we give priority to the species that participate in the pathways that potentially have the largest impact on the community; effectively incorporating, at least partially, the dynamics of the system.

@@

We then specified the structure of all networks using pollinator visitation frequency, which has been shown to be an appropriate surrogate for interspecific effects in pollination networks [@Vazquez2005; @Bascompte2006]. 
To examine whether this decision would influence our results, we also evaluated the effect of using pollinator efficiency or pollinator importance as alternative measures of species interactions in a different data set that lacked invasive species [@NeEman2010; @Ballantyne2015], and we found quantitatively similar results for all three of these options (Supplementary Information XXX).
Furthermore, because our approach depends to a large degree on the network topology, we evaluated the robustness of our results to undersampling.
Specifically, we calculated *n~D~*, and species relative importance (see below) for 500 random subsamples of each empirirical network in which the weakest links were more likely to be removed. 
The sensitivity analysis indicated that even in the absence of complete sampling a control theoretic approach can be applied (Supplementary Information XXX).

@@

We began by quantifying the manageability of each of the aforementioned networks.
To do so, we calculated the networks' maximum matching and determined the minimum proportion of species *n~D~* that need external input signals—a management intervention—to fully control the species abundances in the community. 
To simplify the analysis, we only considered the largest component in a network if it had more than one (two species are in different components if there exists no path between them and are hence independent of each other in terms of network control). 
Smaller components were present in eleven out of the twenty networks and were typically composed of just one plant and one pollinator. 
Their removal represented an average loss of `r sp_lost`% of the species and `r int_lost`% of the interactions.

@@

Recall that the aforementioned maximum matching algorithm requires a directed network in which a link between species *i* and *j* pointing to species *j* indicates that the abundance of *j* can be affected by the abundance of *i*.
This implies that we need first to identify a directionality for the links between species that is consistent with the dynamics of the community (Figure 2). 
In some ecological networks, establishing the directionality is relatively straightforward, for example when links represent biomass transfer or energy flow. 
Interspecific effects in pollination networks, however, are not strictly directed since the benefit is mutual between interacting species. 
Nevertheless, the relative extent to which a given pair of interacting species affect each other can be quantified by the magnitude of the mutual dependence [@Bascompte2006]. 
The dependence of plant *i* on pollinator *j*, *d~ij~*, is the proportion of the visits coming from pollinator *j* compared to all pollinator visits to plant *i*. 
Likewise, the dependence of pollinator *j* on plant *i*, *d~ji~*, is the proportion of the visits by pollinator *j* to plant *i* and all visits of pollinator *j*.
As the dependences are not symmetric, their use generates a weighted bipartite network in which all interacting pairs are connected by two directed links (Figure 2b).

```{r figure 2, echo = F, fig.width = 6.2, fig.height = 1.6, message = F, warning = F, fig.pos = "T", fig.cap = "**Different ways to depict quantitative mutualistic networks**. (a) Pollination networks are typically described by the number of visits between each plant and animal species. (b) Given visitation data, the mutual dependences between interacting species are calculated directly based on the relative visitation frequencies. (c) The relative differences of dependences—the interaction asymmetry—then provide a means to identify the dominant direction of the interspecific effects."}

@@

Given the respective dependences, the extent to which a species $i$ affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry given by $$a(i,j) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
Mutual dependences have previously been shown to be highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa). 
This suggests that it may be possible to relax the assumption of bidirectional dependences further and simplify the network such that interacting species are connected by only one directed link when mutual dependences are asymmetric (Figure 2c). 
We found here that changing to unidirectional interactions determined by the observed direction of asymmetry, as a surrogate of bidirectional mutual dependences does not alter the relative *n~D~* of different networks (Supplementary Information XXX). 
Moreover, this simplification confers an additional advantage for our purposes since it dramatically reduces the number of links in the network. 
This translates into a substantial reduction of the time and memory required for the computation of all possible maximum matchings in a network, particularly for large networks (see "Relative importance" subsection below).

Finding the maximum matchings can be an expensive operation especially in large, directed, and highly connected networks.
Although less computationally expensive heuristics to characterise the control profile of complex networks do exist [@Ruths2014], we found their use to be extremely sensitive to assumptions regarding the direction of control (Supplementary Materials Section 2).
Consequently, we have adopted a strategy based on an alternative bipartite representation of the directed network in which the two levels indicate the outgoing and incoming links to each node (Supplementary Section XXX). 
Once we had this alternative representation, then used the maximum bipartite matching algorithm implemented in `igraph` on each empirica [@Csardi2006a].

@@

Although understanding the variability of manageability across ecological networks is a useful result itself, we also wanted to test whether invasion status had an impact on the observed *n~D~*. 
We, therefore, used a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also controlling for factors related to species richness, since one might naively expect to see a negative relationship between diversity and manageability [@Menge1995]. 
These covariates included the total number of species, plant richness, pollinators richness, the ratio of plants to pollinators richness, the link density (connectance), and the study site (as a two-level factor). 
We assessed competing models by comparing the Akaike Information Criterion corrected for small sample sizes (AICc), and report results for the most parsimonious model.

We next explored whether real networks differ in their architecture from random ones in a concerted way that affects manageability. 
Previous research indicates a direct link between a network's degree distribution and the number of nodes necessary to fully control it [@Liu2011], but the strength and applicability of this relationship have not been tested for in weighted ecological networks. 
We therefore compared the driver node density *n~D~* of the empirical networks to networks generated by a null model that maintained each species' strength (its total sum of visits) while allowing their degrees (its number of interactions) to vary. 
Randomisations were generated using vegan 2.3-3 [@Oksanen2016]. 
After generating the randomised networks, we then calculated the mutual dependences and interaction asymmetries of each and determined *n~D~*  using our maximum matching framework.
Finally, we calculated the average rank (akin to a p-value) of *n~D~* for each empirical network compared to the corresponding one of each set of 999 randomisations.

Beyond network structure, the dependence asymmetry plays a fundamental role in determining the direction of control in each two-species interaction and therefore has the potential to influence the network *n~D~* results above. 
We, therefore, performed an additional randomisation in which we kept the structure of network constant but randomised the direction of the interaction asymmetries. 
That is, we first calculated the observed asymmetries for each community and then shuffled the direction of the link between each pair of species. 
Similar to the other null models, we calculated the average rank of the empirical *n~D~* when compared to that of the randomisations.

@@

Our second key question is related to how species differ in their ability to drive the population dynamics of the community. 
To quantify this importance we computed all maximal cardinality matchings in each network. 
We then calculated the frequency with which each species *i* is deemed to be a driver (*f~D~*) or a superior node (*f~S~*) in the set of matchings that had a matching weight greater or equal to 0.5 times the weight of the maximum matching. 
We selected this threshold as it provided a high agreement between networks quantified by visitation and pollination efficiency as well as between our weighting/directionality assumptions; however, the choice of this threshold had a negligible impact on any results (Supplementary Information XXX).

Even in sparse networks, like those studied here, the number of maximal matchings increases exponentially with the number of links and nodes in a network. 
Unfortunately, this means that the large number of links in the most diverse communities rendered the computation unfeasible when we used mutual dependences. 
Taking this limitation into account, we compared the relative species ranks obtained when using asymmetries to those found when using mutual dependences to test if they gave consistent results. 
The comparison was performed for eleven of the twenty networks (those for which the number of matchings was smaller than 4 x 10^10^), using a paired Spearman correlation test, a weighted correlation coefficient *r~w2~* [which gives more weight to higher ranks; @PintoDaCosta2015], and a Jaccard similarity of the driver species in both approaches. 
All three approaches identified a high similarity in relative ranks (STILL NEED TO CHECK THAT FOR BOTH *f~D~* AND *f~S~*). 
Consequently, we focused on the results when using the asymmetries rather than mutual dependences when further investigating the factors that determine species' relative importance since this also allows us to obtain results for all 20 networks.

To compute all the maximum cardinality matchings, we first generate the network's line graph—another representation in which nodes are the links of the original network and links represent common ending points [@West2001]. 
We then calculate the complement of this line graph, which generates a graph in which nodes are connected if and only if they are not connected in the line graph. 
Finally, all possible maximal cardinality matchings can be found by enumerating every clique (subgraphs in which all nodes are fully connected to each other) of size *D* in this complement graph [@Csardi2006a; @Gutin2013].
A graphical representation of this procedure can be found in Supplementary Information Fig XX.

@@

We then examined whether some species-level structural properties can predict our metrics of species importance—the frequency to which a species is a driver or a superior node (*f~D~* and *f~S~* respectively).
We used a set of generalised linear mixed-effects models (with binomial error structure) with the relative frequencies as the response variables. 
As predictors in this model, we included measures of centrality (degree and eigen-centrality), which have been found to be strong predictors of importance in a coextinction context [@Memmott2004]; a measure related to network robustness (contribution to nestedness), as nestedness has been proposed as one of the key properties that promote stability in mutualistic networks [@Saavedra2011]; and two measures of strength of association and dependence (visitation and dependence strength), as their distribution determines the extent of interspecific effects [@Bascompte2006].
In addition, we also included guild and invasive status as categorical fixed effects.
Although the importance of plants and pollinators or invasive and non-invasive species could respond differently to our structural metrics, our data set did not contain enough variation to include the corresponding interactions terms for these latter two predictors. 
All network metrics were calculated using the R package bipartite 2.06 [@Dormann2008]. 
We lastly allowed for variation between different communities by including the network identity as a random effect [@Bates2015]. 
Candidate models were compared using AICc and the relative importance of the explanatory variables was evaluated using the sum of Akaike weights over candidate models that accounted for 95% of the evidence [@Burnham2003; @Bates2015; @Barton2016]. 
Coefficient estimates were averaged following @Buckland1997a while confidence intervals were calculated following @Lukacs2010.
